Supplementary of Adversarial Zero-Shot Learning

### 2017-11-19 doc/supplementary.tex
Wrote down the optimization problems for autoencoder+generator and discriminator.

	Given an input image representation $\bb{x}^c \in R^{d_x}$, the encoder encodes it into $\bb{h}^c \in R^{d_h}$ by
	\begin{align}
		\bb{h}^c = \sigma(W^e \bb{x}^c + \bb{b}^e),
	\end{align}
	where $W^e \in R^{d_h \times d_x}$, $\bb{b}^e \in R^{d_h}$, and $\sigma(\cdot)$ is the sigmoid function,
	\begin{align}
		\sigma(s) = \frac{1}{1 + e^{-s}},
	\end{align}
	applied element-wisely. Note that the hidden representation space $R^{d_h}$ is also the space of the text representation; that is, $\bb{t}^c \in R^{d_h}$. The decoder computes
	\begin{align}
		\tilde{\bb{x}}^c = \sigma(W^d \bb{h}^c + \bb{b}^d),
	\end{align}
	where $W^d \in R^{d_x \times d_h}$ and $\bb{b}^d \in R^{d_x}$, such that the reconstruction cross entropy,
	\begin{align}
		S = -\bb{x}^c \odot \log \tilde{\bb{x}}^c,
	\end{align}
	where the log being applied element-wisely, is to be minimized.

@@

	For the autoencoder and the generator of the adversarial net, the loss function is the empirical risk,
	\begin{align}
		f_e = \frac{1}{\ell} \sum_{c = 1}^{N_s} \sum_{i = 1}^{\ell_c} \left\{ -\bb{x}^{c, (i)} \odot \log \tilde{\bb{x}}^{c, (i)} + \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right] + || \bb{h}^{c, (i)} - \bb{t}^c ||_2^2 \right\},
	\end{align}
	where
	\begin{align}
		\ell = \sum_{c = 1}^{N_s} \ell_c
	\end{align}
	is the total number of training images. Here we assume there is only one text $\bb{t}^c$ for each class.

	where the parameters of the discriminator is held constant.

	\begin{align}
		f = \frac{1}{\ell} \sum_{i = 1}^{\ell} \log z^{2, (i)}
	\end{align}

>>>>

	Given an input image representation $\bb{x}^c \in R^{d_x}$, the encoder encodes it into $\bb{h}^c \in R^{d_h}$ by
	\begin{align}
		\bb{h}^c = \sigma(W^e \bb{x}^c + \bb{b}^e),
	\end{align}
	where $W^e \in R^{d_h \times d_x}$, $\bb{b}^e \in R^{d_h}$, and $\sigma(\cdot)$ is the sigmoid function,
	\begin{align}
		\sigma(s) = \frac{1}{1 + e^{-s}},
	\end{align}
	applied element-wisely. Note that the hidden representation space $R^{d_h}$ is also the space of the text representation; that is, $\bb{t}^c \in R^{d_h}$. The decoder computes
	\begin{align}
		\tilde{\bb{x}}^c = \sigma(W^d \bb{h}^c + \bb{b}^d),
	\end{align}
	where $W^d \in R^{d_x \times d_h}$ and $\bb{b}^d \in R^{d_x}$, such that the reconstruction cross entropy,
	\begin{align}
		S = -\bb{x}^c \odot \log \tilde{\bb{x}}^c,
	\end{align}
	is minimized. Here $\odot$ denotes the element-wise product, and the log function is applied element-wisely.

@@

	For the autoencoder and the generator of the adversarial net, the loss function is the empirical risk,
	\begin{align}
		f_g = \frac{1}{m} \sum_{c = 1}^{N_s} \sum_{i = 1}^{m_c} \left\{ -\bb{x}^{c, (i)} \odot \log \tilde{\bb{x}}^{c, (i)} + \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right] + || \bb{h}^{c, (i)} - \bb{t}^c ||_2^2 \right\},
	\end{align}
	where
	\begin{align}
		m = \sum_{c = 1}^{N_s} m_c
	\end{align}
	is the total number of training images. Here we assume there is only one text $\bb{t}^c$ for each class.

	For the discriminator of the adversarial net, the loss function is the empirical risk,
	\begin{align}
		f_d = -\frac{1}{m} \sum_{j = 1}^{m} \log D( \bb{z}^{(j)} ) - \frac{1}{m} \sum_{c = 1}^{N_s} \sum_{i = 1}^{m_c} \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right],
	\end{align}
	where $\bb{z}^{(j)}$ are $m$ samples drawn from the prior distribution $\mathcal{N}(0, \lambda^2)$.

	The optimization problem for the autoencoder and the generator is
	\begin{align}
		\min_{W^e, \bb{b}^e, W^d, \bb{b}^d} \; f_g,
	\end{align}
	while the parameters of the discriminator ($W^1, \bb{b}^1, \bb{w}^2, b^2$) are held constant. The optimization problem for the discriminator is
	\begin{align}
		\min_{W^1, \bb{b}^1, \bb{w}^2, b^2} \; f_d,
	\end{align}
	while the parameters of the generator ($W^e, \bb{b}^e, W^d, \bb{b}^d$) are held constant.
